ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-08 pyked.tex
Add more standards URLs to the text instead of footnotes

More recently, Varga and coworkers~\autocite{Varga2015a,Varga2017} developed the
ReSpecTh standard, which builds on the PrIMe format. ReSpecTh adds important
features that make files better standalone representations of experimental
data---i.e., more informative by themselves rather than in concert with a larger
system. For example, where PrIMe uses internal bibliographic references,
ReSpecTh adds a field for typical bibliographic data, including the DOI of
the cited article. The ReSpecTh standard also
provides machine-readable formats for describing ignition experiments, including
a field for the definition of autoignition and the ability to specify
facility-specific effects. It can also describe speciation measurements in
perfectly stirred reactors, flow reactors, and burner-stabilized flames, as well as
burning velocity data. To support this, ReSpecTh files allow the specification of species by
standard identifiers, including InChI or SMILES. Finally, each ReSpecTh file
has a unique DOI and URL assigned to it.

@@

Despite the development of these standards, limited examples exist in the
literature of open data \emph{sharing} using the formats. To the best
of our knowledge, the largest such publicly available database is hosted by
the Clean Combustion Research Center at King Abdullah University of Science and
Technology (KAUST): CloudFlame.\footnote{\url{https://cloudflame.kaust.edu.sa}}
Started in 2013~\autocite{Goteng:2013cf,Goteng:2014,ReynoChiasson:2015}, CloudFlame
serves as an openly accessible database for experimental data, available in a standard
CSV format, and also provides a cloud infrastructure for running simulations
based on stored models and data. While an admirable and useful effort,
CloudFlame, like ReSpecTh and PrIMe, is a closed system controlled by a single
institution rather than by the community at large.

>>>>

More recently, Varga and coworkers~\autocite{Varga2015a,Varga2017} developed the
ReSpecTh standard (available at
\url{http://respecth.chem.elte.hu/respecth/reac/CombustionData.php}),
which builds on the PrIMe format. ReSpecTh adds important
features that make files better standalone representations of experimental
data---i.e., more informative by themselves rather than in concert with a larger
system. For example, where PrIMe uses internal bibliographic references,
ReSpecTh adds a field for typical bibliographic data, including the DOI of
the cited article. The ReSpecTh standard also
provides machine-readable formats for describing ignition experiments, including
a field for the definition of autoignition and the ability to specify
facility-specific effects. It can also describe speciation measurements in
perfectly stirred reactors, flow reactors, and burner-stabilized flames, as well as
burning velocity data. To support this, ReSpecTh files allow the specification of species by
standard identifiers, including InChI or SMILES. Finally, each ReSpecTh file
has a unique DOI and URL assigned to it.

@@

Despite the development of these standards, limited examples exist in the
literature of open data \emph{sharing} using the formats. To the best
of our knowledge, the largest such publicly available database is hosted by
the Clean Combustion Research Center at King Abdullah University of Science and
Technology (KAUST): CloudFlame (available at \url{https://cloudflame.kaust.edu.sa}).
Started in 2013~\autocite{Goteng:2013cf,Goteng:2014,ReynoChiasson:2015}, CloudFlame
serves as an openly accessible database for experimental data, available in a standard
CSV format, and also provides a cloud infrastructure for running simulations
based on stored models and data. While an admirable and useful effort,
CloudFlame, like ReSpecTh and PrIMe, is a closed system controlled by a single
institution rather than by the community at large.
